Active Learning for SAT Solver Benchmarking

### 2022-10-11 paper/paper.tex
algo1

In this section, we present the details of our approach.
Section~\ref{sec:main:framework} describes the general framework.
Section~\ref{sec:main:model} specifies the details of the underlying prediction model and describes how we may derive a solver ranking from that model.
We discuss possible criteria for sampling instances in Section~\ref{sec:main:sampling}.
Section~\ref{sec:main:stopping} concludes with possible stopping conditions.

\subsection{Incremental Benchmarking Framework}
\label{sec:main:framework}

Our framework to score a new solver~$\hat{a}$ follows a three-step procedure, outlined in Algorithm~\ref{algALBenchmark}:
While the stopping condition is not met (line~1), we select \emph{one} SAT instance from the pool of instances with the help of a prediction model~$\mathcal{M}$ (line~2) and evaluate the new solver~$\hat{a}$ on this instance (line~3).
We then use the acquired result to update the prediction model~$\mathcal{M}$ (line~4).
When the stopping criterion is met, we return the predicted score of the new solver~$\hat{a}$ (line~5).

Since the potential runtime of experiments is by magnitudes larger than the model's update time, we only consider incrementing our benchmark by one instance at a time rather than using batches, which is also proposed in current active-learning advances~\cite{SinhaED19,2019gaal}.

@@

  %\KwIn{Instances $\mathcal{I}$, Solvers $\mathcal{A}$, Runtimes $r\!: \mathcal{A} \times \mathcal{I} \rightarrow \left[0, \tau\right]$}
  \KwIn{Model $\mathcal{M}$,  Solver $\hat{a}$}
  \KwOut{Score of $\hat{a}$}

@@

  %$\mathcal{M} \leftarrow \textrm{init model with $\mathcal{A}$, $\mathcal{I}$, $r$, and $\hat{a}$}$
  %$\tilde{\mathcal{I}} \leftarrow \emptyset$

  \While(\tcp*[f]{cf. Section~\ref{sec:main:stopping}}){$\operatorname{not} \, \operatorname{stop}\!\left(\mathcal{M}\right)$}{
    $s \leftarrow \operatorname{selectNextInstance}\!\left(\mathcal{M}\right)$ \tcp*{cf. Section~\ref{sec:main:sampling}}

    $t \leftarrow \operatorname{runExperiment}\!\left(\hat{a},\,  s\right)$  \tcp*{Runs $\hat{a}$ on $s$ with time-out $\tau$}

    %$\tilde{\mathcal{I}} \leftarrow \tilde{\mathcal{I}} \cup \left\lbrace s \right\rbrace$

    $\operatorname{updateModel}\!\left(\mathcal{M},\, s,\, t\right)$ \tcp*{cf. Section~\ref{sec:main:model}}
  }

  \Return $\operatorname{predictScore}\!\left(\mathcal{M}\right)$ \tcp*{cf. Section~\ref{sec:main:model}}

@@

\subsubsection{Wilcoxon Stopping Criterion}

@@

\subsubsection{Model Convergence Stopping Criterion}

>>>>

The outline of our benchmarking framework is depicted in Algorithm~\ref{algALBenchmark}. 
Given a set of known solvers $\mathcal{A}$, instances $\mathcal{I}$ and runtimes $r$, we first create a prediction model~$\mathcal{M}$ for the new solver $\hat a$ (Line~1). 
The prediction model is used to repeatedly select an instance (Line~4) for benchmarking $\hat a$ (Line~5). 
The acquired result is subsequently used to update the prediction model~$\mathcal{M}$ (Line~6). 
When the stopping criterion is met (Line~3), we quit the benchmarking loop and predict the final score of $\hat a$ (Line~8). 
Algorithm~\ref{algALBenchmark} returns the predicted score of $\hat a$ as well as the acquired runtime measurements (Line~9).

Section~\ref{sec:main:model} specifies the details of the underlying prediction model and describes how we may derive a solver ranking from that model.
We discuss possible criteria for sampling instances in Section~\ref{sec:main:sampling}.
Section~\ref{sec:main:stopping} concludes with possible stopping conditions.

% MI: This belongs to discussion at the end since this also has substantial disadvantages:
Since the potential runtime of experiments is by magnitudes larger than the model's update time, we only consider incrementing our benchmark by one instance at a time rather than using batches, which is also proposed in current active-learning advances~\cite{SinhaED19,2019gaal}.

@@

  %\KwIn{Instances $\mathcal{I}$, Solvers $\mathcal{A}$, Runtimes $r\!: \mathcal{A} \times \mathcal{I} \rightarrow \left[0, \tau\right]$}
  \KwIn{Solvers $\mathcal{A}$, Instances $\mathcal{I}$, Runtimes $r : \mathcal{A} \times \mathcal{I} \rightarrow [0, \tau]$, Solver $\hat{a}$}
  \KwOut{Predicted Score of $\hat{a}$, Measured Runtimes $\mathcal{R}$}

@@

  $\mathcal{M} \leftarrow \operatorname{initModel}(\mathcal{A}, \mathcal{I}, r, \hat{a})$ \;

  \BlankLine
  $\mathcal{R} \leftarrow \emptyset$ \;
  \While(\tcp*[f]{cf. Section~\ref{sec:main:stopping}}){$\operatorname{not} \operatorname{stop}(\mathcal{M})$}{
    $e \leftarrow \operatorname{selectNextInstance}\!\left(\mathcal{M}\right)$ \tcp*{cf. Section~\ref{sec:main:sampling}}

    $t \leftarrow \operatorname{runExperiment}\!\left(\hat{a},\,  e\right)$  \tcp*{Runs $\hat{a}$ on $e$ with time-out $\tau$}

    $\operatorname{updateModel}\bigr(\mathcal{M}, (e, t)\bigl)$ \tcp*{cf. Section~\ref{sec:main:model}}

    \BlankLine
    $\mathcal{R} \leftarrow \mathcal{R} \cup \bigl\{ (e, t) \bigr\}$
  }
  $s \leftarrow \operatorname{predictScore}(\mathcal{M})$ \tcp*{cf. Section~\ref{sec:main:model}}

  \BlankLine
  \Return $(s, \mathcal{R})$

@@

\subsubsection{Wilcoxon Stopping Criterion.}

@@

\subsubsection{Model Convergence Stopping Criterion.}
